Multispecies survey for diet comp

### 2020-12-04 SurveyDietCompTest.Rmd
draft sample_diet seems to work

dat <- survey_cons
#dat <- diettest

@@

  dat3 <- left_join(dat2, fgsprey) %>%
    rowwise() %>%
    mutate(unidprop = runif(1, 0, unidprey*atoutput),
           sampprop = atoutput - unidprop)

@@

  unidrows <- dat3 %>%
    #select(-atoutput, -prey, -sampprop) %>%
    group_by(species, time.days, agecl, unidtype) %>%
    summarise(unidtot = sum(unidprop)) %>%
    ungroup() %>%
    rename(prey = unidtype, sampprop = unidtot)

@@

	#tidy
	dietprop <- dat2 %>%
	  group_by(species, time.days, agecl) %>%
	  do(mutate(., dietSamp = DirichletReg::rdirichlet(1, alphamult * atoutput)))

  # returns diet proportions with observation error: Dirichlet, and bias from unknown id and/or family level aggregation

  return(dietprop)
}

>>>>

dat <- survey_cons
#dat <- diettest
unidprey <- 0.5 #0 makes none unid, 1 could be all, reflects max proportion to unid
alphamult <- 10000000 #default is almost identical to true, smaller more variable

@@

  dat2 <- left_join(dat2, fgsprey) %>%
    rowwise() %>%
    mutate(unidprop = runif(1, 0, unidprey*atoutput),
           sampprop = atoutput - unidprop)

@@

  unidrows <- dat2 %>%
    #select(-atoutput, -prey, -sampprop) %>%
    group_by(species, time.days, agecl, unidtype) %>%
    summarise(unidtot = sum(unidprop)) %>%
    ungroup() %>%
    rename(prey = unidtype, sampprop = unidtot)

  dat2 <- dat2 %>%
    select(species, time.days, agecl, prey, sampprop) %>%
    full_join(unidrows)

@@

	#tidy
	dat2 <- dat2 %>%
	  filter(sampprop>0) %>%
	  group_by(species, time.days, agecl) %>%
	  do(mutate(., dietSamp = DirichletReg::rdirichlet(1, alphamult * sampprop))) %>%
    ungroup() %>%
    select(-sampprop)

  # returns diet proportions with observation error: Dirichlet, and bias from unknown id

  return(dat2)
}
